\documentclass{article}

\usepackage{amssymb}
\usepackage{calc}
\usepackage[margin={1in,1in}]{geometry}
\usepackage{enumitem}
\usepackage{fixltx2e}
\usepackage[unicode]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{textcomp}
\usepackage[table]{xcolor}
\usepackage{gensymb}
\usepackage{tabularx}
\usepackage{titling}

\title{Brewing Procedures}
\author{}
\date{}

\begin{document}
  \setlength{\parindent}{0pt}
  \setlength{\parsep}{0pt}
  \setlength{\multicolsep}{1mm}
  \setlength{\fboxsep}{0pt}
  \setlength{\fboxrule}{0pt}

  \rowcolors{1}{gray!20!white}{gray!35!white}

  \fontfamily{phv}\selectfont%

  \newenvironment{cldescription}{\begin{description}[topsep=0pt,noitemsep,leftmargin=0pt,label={}]\fontfamily{phv}}{\normalfont\end{description}}

  \newenvironment{clitemize}{\begin{itemize}[topsep=0pt,noitemsep,leftmargin=0pt,label={}]}{\end{itemize}}
  \newcommand{\clitem}[2]{\item#1 \dotfill \textbf{#2}}

  \newlist{packlist}{itemize}{1}
  \setlist[packlist]{noitemsep,topsep=0pt,leftmargin=1.55em,label=$\square$}

  \newlist{notelist}{itemize}{1}
  \setlist[notelist]{noitemsep,topsep=0pt,leftmargin=1.55em,label=\scriptsize$\blacksquare$}

  \newcommand{\colorlistbox}[2]{\colorbox{#1}{\parbox{\linewidth}{#2}}}
  \newcommand{\internationalbox}[1]{\colorlistbox{green!60!black}{#1}}
  \newcommand{\packlistbox}[1]{\colorlistbox{green!20!white}{\partnote{PACK LIST}#1}}

  \newcommand{\columnnote}[2]{\color{white}\colorbox{#1}{\strut\makebox[\columnwidth]{\raisebox{-1pt}{#2}}}\color{black}}
  \newcommand{\importantnote}[1]{\columnnote{red!80!black}{#1}}
  \newcommand{\partnote}[1]{\columnnote{green!60!black}{#1}}

  \newcommand{\columnheading}[2]{\color{white}\colorbox{#1}{\strut\makebox[\columnwidth]{\raisebox{-1pt}{\textbf{#2}}}}\color{black}}
  \newcommand{\partheading}[1]{\columnheading{green!80!red}{#1}}
  \newcommand{\checklistheading}[1]{\color{white}\columnheading{black}{#1}\color{black}}
  \newcommand{\emptyheading}{\columnheading{white}{}}

  \newcommand{\importantheading}[1]{\columnheading{red!80}{#1}}

  \begin{titlingpage}
    \maketitle
  \end{titlingpage}

  \pagebreak

  {\LARGE Contents}

  \begin{enumerate}
    \item Brew Day
    \begin{enumerate}[label*=\arabic*.]
      \item Equipment \& Materials \dotfill \textbf{2}
      \item Brew \dotfill \textbf{2}
    \end{enumerate}
  \end{enumerate}

  \pagebreak%

  {\Large \checklistheading{BREW DAY}}

  \begin{multicols*}{2}
    \checklistheading{EQUIPMENT \& MATERIALS}

    \partheading{WEEK OF}
    \begin{clitemize}
      \clitem{Recipe}{DECIDE}
      \clitem{Grains \& hops}{ORDER}
      \clitem{Propane}{FILL}
    \end{clitemize}

    \partheading{DAY BEFORE}
    \begin{clitemize}
      \clitem{Lighter}{CHARGE}
      \clitem{Brew table}{CLEAN}
      \clitem{Brew kettle}{CLEAN}
      \clitem{MLT}{CLEAN}
      \clitem{HLT}{CLEAN}
      \clitem{Vorlauf pitcher}{CLEAN}
      \clitem{Hoses}{COLLECT \& CLEAN}
      \clitem{Brew area}{CLEAN}
      \clitem{Ice}{BUY}
      \clitem{Distilled water}{$\geq$ 12 GAL.}
    \end{clitemize}

    \partheading{DAY OF}
    \begin{clitemize}
      \clitem{Recipe materials}{PICK UP}
      \clitem{Grains}{WEIGH}
    \end{clitemize}

    \checklistheading{BREW}

    \begin{clitemize}
      \clitem{Yeast}{REMOVE FROM FRIDGE}
      \clitem{Windows}{OPEN}
      \clitem{Fans}{PLACE \& TURN ON}
      \clitem{Brew kettle}{FILL WITH 4--5 GAL. DIST. WATER}
      \clitem{Propane}{CONNECT TO BURNER}
      \clitem{Burner}{START}
      \clitem{Water}{HEAT TO REQ. STRIKE TEMP.}
      \clitem{Grist}{COMBINE IN GRAIN BUCKET}
      \clitem{MLT \& HLT}{SETUP}
      \partnote{WAIT FOR STRIKE WATER TO HEAT}
      \clitem{Strike water}{ADD REQ. AMT. TO MLT}
      \clitem{Burner}{OFF}
      \clitem{Grist}{SLOWLY ADD TO MLT WHILE STIRRING}
      \importantnote{AVOID CLUMPS}
      \clitem{MLT}{COVER}
      \clitem{MLT temp.}{NOTE}
      \clitem{Timer}{START}
      \clitem{Brew kettle}{FILL WITH 6.5 GAL. DIST. WATER}
      \clitem{Burner}{START}
      \partnote{WAIT FOR SPARGE WATER TO HEAT}
      \clitem{Sparge water}{TRANSFER TO HLT}
      \clitem{HLT}{MOVE ABOVE MLT}
      \clitem{HLT temp.}{NOTE}
      \clitem{Sparge arm}{CONNECT TO HLT}
      \partnote{WAIT FOR MASH TO COMPLETE}
      \clitem{Drain hose}{CONNECT TO MLT}
      \clitem{Vorlauf}{AS REQ.}
    \end{clitemize}

  \end{multicols*}
\end{document}
